Amphibians

### 2024-04-25 analysis/07_study_change.Rmd
Rename, move

change_groups <- wide_table %>% 
  select(study_id, S, Jaccard_base, FRic, FEve, FDiv) %>%
  mutate(across(!study_id, ~case_when(
    . > 0 ~ "pos",
    . < 0 ~ "neg",
    .default = "0"
  )))

change_group_count <- change_groups %>%
  select(-study_id) %>%
  group_by(across(everything())) %>%
  count()

no_change <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id, ~. == 0)) %>%
  left_join(meta_clean)

>>>>

all_metrics <- c("S", "Jaccard_base", "FRic", "FEve", "FDiv", "SES_FRic", "SES_FEve", "SES_FDiv")

change_groups <- wide_table %>% 
  select(study_id,all_of(all_metrics)) %>%
  mutate(across(!study_id, ~case_when(
    . > 0 ~ "pos",
    . < 0 ~ "neg",
    .default = "0"
  )))

change_group_count <- change_groups %>%
  select(-study_id, -starts_with("SES_")) %>%
  group_by(across(everything())) %>%
  count()

change_group_count_ses <- change_groups %>%
  select(-c(study_id, FRic, FEve, FDiv)) %>%
  group_by(across(everything())) %>%
  count()

change_group_count_complete <- change_groups %>%
    select(-c(study_id)) %>%
    group_by(across(everything())) %>%
    count() %>%
  mutate(change_description = case_when(
    S == "pos" ~ "increase in richness, not beyond random expectation", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" & Jaccard_base == "neg" ~ "changes in functional space due to turnover",
    n == 6 ~ "no change", 
    .default = NA
  ))

change_group_ses_desc <- change_group_count_ses %>%
   mutate(change_description = case_when(
    S == "pos" ~ "increase in species richness, sometimes leading to increase in functional richness", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" ~ "functional change independent of species richness change",
    n == 7 ~ "no change", 
    .default = NA
  ))
```

```{r}
no_change <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id, ~. == 0)) %>%
  left_join(meta_clean)

### 2024-04-25 analysis/08_amphibian_trends.Rmd
Rename, move

---
title: "Sensitivity Analysis"
output: html_document
date: "2022-08-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

load(here::here("data/model_data.rda"))
#exclude amphibians
model_data <- model_data %>% filter(taxa != "Amphibians")
```

Let's test the sensitivity of the general trends (and study level patterns?) to major data processing decisions.

@@

  return(fit_trends)
}
```

Define models to fit
```{r}
metric_names <- unique(model_data$metric)
raw_metrics <- c("SES_FRic", "SES_FDiv", "SES_FEve", 
                 "CWM_diet_inv", "CWM_forstrat_ground", "CWM_forstrat_watbelowsurf", "FEve")
log_metrics <- c("FRic", "S", "FDiv")
logone_metrics <- metric_names[!metric_names %in% c(raw_metrics, log_metrics)]

@@

1. Min time series duration
```{r}
dur_dfs <- list(min3 = filter(model_data, duration > 2),
                min4 = filter(model_data, duration > 3),
                min5 = filter(model_data, duration > 4))

duration_sens <- map_dfr(dur_dfs, ~pmap_dfr(filter(mods, model_id == "base"), get_model, data = .x), .id = "dataID")
```

2. Trait Coverage
```{r}
load(here::here("data/study_table.rda"))

model_data <- model_data %>%
  left_join(study_table %>% select(study_id, coverage) %>% mutate(study_id = as.factor(study_id)))

covg_dfs <- list(covg75 = filter(model_data, taxa != "Amphibians"),
                covg85 = filter(model_data, taxa != "Amphibians", coverage >= 0.85),
                covg90 = filter(model_data, taxa != "Amphibians", coverage >= 0.90))

coverage_sens <- map_dfr(covg_dfs, ~pmap_dfr(filter(mods, model_id == "base"), 
                                             get_model, data = .x), .id = "dataID")

sens_mods <- bind_rows(duration_sens, coverage_sens) %>%
  select(-model) %>%
  filter(metric != "Jaccard_next")

usethis::use_data(sens_mods)

write_csv(sens_mods, here::here("paper", "sensitivity_models.csv"))
```

>>>>

---
title: "Amphibians"
output: html_document
date: "2023-06-22"
---

@@

load(here::here("data/model_data.rda"))
amph_data <- model_data %>%
  filter(taxa == "Amphibians")
```

@@

  return(fit_trends)
}
````

```{r}
metric_names <- unique(model_data$metric)
raw_metrics <- c("SES_FRic", "SES_FDiv", "SES_FEve", 
                 "CWM_diet_inv", "CWM_forstrat_ground", "CWM_forstrat_watbelowsurf", "FEve")
log_metrics <- c("FRic", "S", "FDiv")
logone_metrics <- metric_names[!metric_names %in% c(raw_metrics, log_metrics)]

@@

```{r}
#Fit models with base settings
mod_results <- pmap_dfr(mods %>% filter(model_id == "base"), get_model, data = amph_data) %>%
  mutate(REML = TRUE, bobyqa = FALSE)

#manuscript table
mod_results %>% 
  filter(model_id == "base") %>% 
  select(-c(model_id, warning, statistic, df)) %>% 
  readr::write_csv(here::here("figures", "amph_model_table.csv"))
```
